Exploring Local Explanations of Non-linear Models Using Animated Linear Projections

### 2022-01-12 _paper.rmd
revised wording on penguins example to clarify subset

The Palmer penguins data [@gorman_ecological_2014; @horst_palmerpenguins_2020] was collected on three species of penguins foraging near Palmer Station, Antarctica. The data was publicly available to be a substitute for the overly-used iris data, and is quite similar in form. There are 330 observations and we will use the four physical measurements, `bill_length_mm` (`b_l`), `bill_depth_mm` (`b_d`), `flipper_length_mm` (`f_l`), `body_mass_g` (`wgt`), for this illustration. A random forest model was fitted with species as the response variable.

>>>>

The Palmer penguins data [@gorman_ecological_2014; @horst_palmerpenguins_2020] was collected on three species of penguins foraging near Palmer Station, Antarctica. The data was publicly available to be a substitute for the overly-used iris data, and is quite similar in form. The subset used here has missing values removed (as used in the `spinifex` package), and there are 333 observations and four physical measurements, `bill_length_mm` (`b_l`), `bill_depth_mm` (`b_d`), `flipper_length_mm` (`f_l`), `body_mass_g` (`wgt`), for this illustration. A random forest model was fitted with species as the response variable.

### 2022-01-12 _paper.tex
revised wording on penguins example to clarify subset

The Palmer penguins data (Gorman, Williams, and Fraser 2014; Horst, Hill, and Gorman 2020) was collected on three species of penguins foraging near Palmer Station, Antarctica. The data was publicly available to be a substitute for the overly-used iris data, and is quite similar in form. There are 330 observations and we will use the four physical measurements, \texttt{bill\_length\_mm} (\texttt{b\_l}), \texttt{bill\_depth\_mm} (\texttt{b\_d}), \texttt{flipper\_length\_mm} (\texttt{f\_l}), \texttt{body\_mass\_g} (\texttt{wgt}), for this illustration. A random forest model was fitted with species as the response variable.

>>>>

The Palmer penguins data (Gorman, Williams, and Fraser 2014; Horst, Hill, and Gorman 2020) was collected on three species of penguins foraging near Palmer Station, Antarctica. The data was publicly available to be a substitute for the overly-used iris data, and is quite similar in form. The subset used here has missing values removed (as used in the \texttt{spinifex} package), and there are 333 observations and four physical measurements, \texttt{bill\_length\_mm} (\texttt{b\_l}), \texttt{bill\_depth\_mm} (\texttt{b\_d}), \texttt{flipper\_length\_mm} (\texttt{f\_l}), \texttt{body\_mass\_g} (\texttt{wgt}), for this illustration. A random forest model was fitted with species as the response variable.
